Cooperative Kernels: Safe Multitasking for Blocking Algorithms on GPUs

### 2016-11-11 write-ups/PLDI/paper.tex
fixed cooperative kernel to use 2 barriers and added line numbers

\paragraph{Adapting graph traversal} \ADComment{Tyler, the original had two global barriers; the port has just one resizing barrier.  Is this right?}
\myfiglong\ref{fig:cgraphsearch} shows a cooperative version of the graph traversal kernel
of \myfig\ref{fig:graphsearch}, introduced in
\mysec\ref{sec:openclexamples}.  
On line~\ref{line:cgraph:resizing}, we change the original global barrier
into a resizing barrier. Several variables are marked to be
transmitted in the case of workgroups joining at the resizing barrier
(lines~\ref{line:cgraph:transmit1}, \ref{line:cgraph:transmit2} and
\ref{line:cgraph:transmit3}): $\keyword{level}$ must be restored so that
new workgroups know which frontier they are processing; $\keyword{in\_nodes}$ and $\keyword{out\_nodes}$ must be restored so that new
workgroups know which of the node arrays are input and output. Lastly,
the static work distribution of the original kernel is no longer valid
in a cooperative kernel. This is because the stride (which is based on
$M$) may change after each resizing barrier
call. To fix this, we re-distribute the work after each resizing
barrier call by recomputing the thread id and stride
(lines~\ref{line:cgraph:rechunking1} and
\ref{line:cgraph:rechunking2}).  \ADComment{Tyler: can you please add the line number references in the following?} This example exploits the fact that the cooperative kernel does not issue $\offerkill$ nor $\offerfork$ directly: the value of $\keyword{stride}$ obtained from $\getglobalsize()$ at line~\ref{...} is stable until the next resizing barrier at line~\ref{...}, and in particular can be safely used inside the $\keyword{for}$ loop.

@@

    level++;
    swap(in_nodes, out_nodes);
    reset(out_nodes);
(*@\label{line:cgraph:resizing}@*)    resizing_global_barrier();
  }
}
\end{lstlisting}
\caption{Cooperative version of the graph traversal kernel of \myfig\ref{fig:graphsearch}, using a resizing global barrier and $\transmit$ annotations}\label{fig:cgraphsearch}
\end{figure}

>>>>

\paragraph{Adapting graph traversal} 
\myfiglong\ref{fig:cgraphsearch} shows a cooperative version of the
graph traversal kernel of \myfig\ref{fig:graphsearch}, introduced in
\mysec\ref{sec:openclexamples}.  On lines~\ref{line:cgraph:resizing1}
and ~\ref{line:cgraph:resizing2}, we change the original global
barriers into a resizing barriers. Several variables are marked to be
transmitted in the case of workgroups joining at the resizing barriers
(lines~\ref{line:cgraph:transmit1}, \ref{line:cgraph:transmit2} and
\ref{line:cgraph:transmit3}): $\keyword{level}$ must be restored so
that new workgroups know which frontier they are processing;
$\keyword{in\_nodes}$ and $\keyword{out\_nodes}$ must be restored so
that new workgroups know which of the node arrays are input and
output. Lastly, the static work distribution of the original kernel is
no longer valid in a cooperative kernel. This is because the stride
(which is based on $M$) may change after each resizing barrier
call. To fix this, we re-distribute the work after each resizing
barrier call by recomputing the thread id and stride
(lines~\ref{line:cgraph:rechunking1} and
\ref{line:cgraph:rechunking2}). This example exploits the fact that
the cooperative kernel does not issue $\offerkill$ nor $\offerfork$
directly: the value of $\keyword{stride}$ obtained from
$\getglobalsize()$ at line~\ref{line:cgraph:rechunking2} is stable
until the next resizing barrier at line~\ref{line:cgraph:resizing1},
and in particular can be safely used inside the $\keyword{for}$ loop.

@@

    swap(&in_nodes, &out_nodes);
(*@\label{line:cgraph:resizing1}@*)    resizing_global_barrier();
    reset(out_nodes);
    level++;
(*@\label{line:cgraph:resizing2}@*)    resizing_global_barrier();
  }
}
\end{lstlisting}
\caption{Cooperative version of the graph traversal kernel of \myfig\ref{fig:graphsearch}, using a resizing global barrier and $\transmit$ annotations}\label{fig:cgraphsearch}
\end{figure}
